Single Cell Xenopus TMT Analysis

### 2020-02-25 Analysis.Rmd
updated

```{r echo=TRUE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
ggplot(pepTidy, aes(log2(intensity), colour = cell)) + geom_density() + theme_bw() + xlim(-20,20)
```

@@

ggpairs(log2(pairs[,2:ncol(pairs)]), lower = list(continuous = wrap("points", alpha = 0.1, size = 0.1))) + theme_bw()
```

@@

ggplot(meanSD, aes(x = log10(mean), y = sd)) + geom_point() + geom_smooth(method = lm, formula = y ~ poly(x, 2))
```

@@

ggplot(pepTidy, aes(log2(intensity), colour = cell)) + geom_density() + theme_bw() + xlim(-8,8)
```

@@

ggpairs(log2(pairs[,2:ncol(pairs)]), lower = list(continuous = wrap("points", alpha = 0.1, size = 0.1))) + theme_bw()
```

@@

mypal = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201))
k = 2
map = pheatmap(cor, show_colnames = F, show_rownames = F, color = mypal, breaks = seq(-1,1, by = 0.01), cutree_cols = k, cutree_rows = k, legend = F)
map

@@

GO <- protImpute %>% dplyr::select(Uniprot) %>% filter(Uniprot %in% keys) %>% 
  rowwise() %>% 
  mutate(GO = mapIds(org.Xl.eg.db, 
                     keys = Uniprot, 
                     keytype = 'UNIPROT', 
                     column = 'GOALL', 
                     multiVals = 'list')) %>% 
  ungroup()

allGO <- tibble(GOterms = unlist(GO$GO) %>% unique())
allGO <- allGO %>% group_by(GOterms) %>% mutate(Uniprot = GO[grep(GOterms, GO$GO),1] %>% as.list()) %>% ungroup()

write_csv(mutate(GO, GO = paste(unlist(GO), sep = '', collapse = ',')), '/Users/kylekovary/Documents/GitHub/Proteome-Expression-Covariation/analysisData/GO.csv')

write_csv(mutate(allGO, Uniprot = paste(unlist(Uniprot), sep = '', collapse = ',')), '/Users/kylekovary/Documents/GitHub/Proteome-Expression-Covariation/analysisData/allGO.csv')

## GO Term Analysis
```{r echo=TRUE, message=FALSE, warning=FALSE}
GO <- read_csv('/Users/kylekovary/Documents/GitHub/Proteome-Expression-Covariation/analysisData/GO.csv') %>% mutate(GO = strsplit(GO, split = ','))

allGO <- read_csv('/Users/kylekovary/Documents/GitHub/Proteome-Expression-Covariation/analysisData/allGO.csv') %>% 
  mutate(Uniprot = strsplit(Uniprot, split = ','),
         GO = mapIds(GO.db, 
                     keys = GOterms, 
                     keytype = 'GOID', 
                     column = 'TERM') %>% as.character(),
         ontology = mapIds(GO.db, 
                     keys = GOterms, 
                     keytype = 'GOID', 
                     column = 'ONTOLOGY') %>% as.character()) %>%
  dplyr::select(GOterms, GO, ontology, everything())

@@

allGO <- allGO %>% group_by(GOterms) %>% dplyr::mutate(cors = corVector(Uniprot, cor) %>% as_tibble() %>% as.list()) %>% ungroup()

x <- allGO %>% rowwise %>% mutate(size = length(Uniprot)) %>% dplyr::select(GOterms, size, cors) %>% unnest() %>% group_by(GOterms) %>% 
  summarise(median = median(cors, na.rm = T),
            sd = sd(cors, na.rm = T),
            size = mean(size)) %>% 
  mutate(GOterms = fct_reorder(GOterms, median))

@@

allGO <- allGO %>% group_by(GOterms) %>% 
  dplyr::mutate(cv = selectCV(Uniprot)) %>% ungroup()

@@

## Cor vs CV
```{r}
test = allGO %>% rowwise() %>% mutate(n = length(Uniprot), medCors = mean(cors), medCV = mean(cv)) %>%
  filter(length(Uniprot) > 3, !is.na(medCors), !is.na(medCV))

>>>>

```{r echo=TRUE, fig.height=5, fig.width=8, message=FALSE, warning=FALSE}
# ggplot(pepTidy, aes(log2(intensity), colour = cell)) + 
#   geom_density() + theme_bw() + xlim(-20,20)
```

@@

# ggpairs(log2(pairs[,2:ncol(pairs)]), 
#         lower = list(continuous = wrap("points", alpha = 0.1, size = 0.1))) + theme_bw()
```

@@

# ggplot(meanSD, aes(x = log10(mean), y = sd)) + geom_point() + geom_smooth(method = lm, formula = y ~ poly(x, 2))
```

@@

# ggplot(pepTidy, aes(log2(intensity), colour = cell)) + geom_density() + theme_bw() + xlim(-8,8)
```

@@

# ggpairs(log2(pairs[,2:ncol(pairs)]), lower = list(continuous = wrap("points", alpha = 0.1, size = 0.1))) + theme_bw()
```

@@

mypal = rev(colorRampPalette(brewer.pal(11, 'RdBu'))(201))
k = 2
map = pheatmap(cor, show_colnames = F, show_rownames = F, color = mypal, breaks = seq(-1,1, by = 0.01), cutree_cols = k, cutree_rows = k, legend = F)
#map

@@

GO <- protImpute %>% dplyr::select(Uniprot) %>% filter(Uniprot %in% keys) %>% 
  mutate(GOterms = mapIds(org.Xl.eg.db, 
                     keys = Uniprot, 
                     keytype = 'UNIPROT', 
                     column = 'GOALL', 
                     multiVals = 'list'))

allGO <- unnest(GO, cols = GOterms) %>% nest(Uniprot = Uniprot) %>%
  rowwise() %>% mutate(n = length(unlist(Uniprot))) %>% ungroup() %>%
  mutate(GO = mapIds(GO.db, 
                     keys = GOterms, 
                     keytype = 'GOID', 
                     column = 'TERM') %>% as.character(),
         ontology = mapIds(GO.db, 
                     keys = GOterms, 
                     keytype = 'GOID', 
                     column = 'ONTOLOGY') %>% as.character()) %>%
  dplyr::select(GOterms, GO, ontology, everything())

# allGO <- tibble(GOterms = unlist(GO$GO) %>% unique())
# allGO <- allGO %>% group_by(GOterms) %>% mutate(Uniprot = GO[grep(GOterms, GO$GO),1] %>% as.list()) %>% ungroup() %>%
#   mutate(
#          GO = mapIds(GO.db, 
#                      keys = GOterms, 
#                      keytype = 'GOID', 
#                      column = 'TERM') %>% as.character(),
#          ontology = mapIds(GO.db, 
#                      keys = GOterms, 
#                      keytype = 'GOID', 
#                      column = 'ONTOLOGY') %>% as.character()) %>%
#   dplyr::select(GOterms, GO, ontology, everything())

@@

allGO <- allGO %>% group_by(GOterms) %>% 
  dplyr::mutate(cors = corVector(Uniprot, cor) %>% as_tibble() %>% as.list(),
                cv = selectCV(Uniprot)) %>% ungroup() %>%
  rowwise() %>% mutate(medCors = mean(cors, na.rm = TRUE),
                       medCV = mean(cv, na.rm = TRUE)) %>%
  ungroup() %>%
filter(length(Uniprot) > 3,
       !is.na(medCors),
       !is.na(medCV))

#saveRDS(GO, 'analysisData/GO.RDS')
#saveRDS(allGO, 'analysisData/allGO.RDS')
```

## GO Term Analysis
```{r echo=TRUE, message=FALSE, warning=FALSE}
#GO <- readRDS('analysisData/GO.RDS')
#allGO <- readRDS('analysisData/allGO.RDS')

x <- allGO %>% rowwise %>% mutate(size = nrow(Uniprot)) %>% dplyr::select(GOterms, size, cors) %>% unnest() %>% group_by(GOterms) %>% 
  summarise(median = median(cors, na.rm = T),
            sd = sd(cors, na.rm = T),
            size = mean(size)) %>% 
  mutate(GOterms = fct_reorder(GOterms, median))

@@

@@

## Cor vs CV
```{r}
test = allGO %>% filter(length(Uniprot) > 3, !is.na(medCors), !is.na(medCV))
